---
title: 'RMarkdown:  In Class Assignment'
author: "John Esparragoza"
date: "Data 2401"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---

```{r setup, include=FALSE}
# Everything in this chunk is R code. 
# You are not expected to understand or edit this yet. 
# We will talk about what this does in a later class, with a little preview in part 2.
knitr::opts_chunk$set(echo = TRUE) 
```

Reminders:

-   You do not need to memorize Markdown syntax.
-   You are expected to look things up using:
    -   RStudio’s Markdown Help
    -   Online documentation or examples
-   Click Knit as you go to check that your document still renders correctly.
-   Commit at the end, but consider committing as you go as well.

# Part 1: Markdown Practice

**Do not skip reading this instruction** Create a new section at the end of this section named "Your work here". In that section, complete the tasks below:

-   Make a *subsection* called Wise Words.
-   Put your favorite quote in a block quote.
-   Add a working, clickable link to a website that provides more information about that quote.
-   Make another *subsection* called "I recommend", and add some information about your favorite author or musician:
    -   A *subsubheading* with the name of the artist or author;\
    -   An example of their writing or lyrics (formatted in a *block of text*);\
    -   A *list* of things they have written or performed (remember to use the formatting markup for a list!), with any of the titles/names in bold.

# My work here

## Wise Words

> "We accept the love we think we deserve"

[link to quote info](https://www.simplypsychology.org/we-accept-the-love-we-think-we-deserve.html)

## I recommend...

### Mac Miller

Lyric sample from "Perfect Circle / Godspeed" :

> "Every devil don't got horns, every hero ain't got capes Open up my eyes, s\*\*\*, I'm finally awake, good mornin' "

-   "Self Care"
-   "2009"
-   "Good News"
-   "Come Back to Earth"

# Part 2: Code Chunks

```{r echo = FALSE}
2 + 2
```

Complete the following steps:

-   Knit the document and observe what appears in the output.
-   Change the chunk option echo=TRUE to echo=FALSE.
-   Knit the document again.
-   Finally, write 2–3 sentences answering the following questions:
    -   What changed between the two outputs?
    -   Did the calculation still run when the code was hidden?
    -   Why might someone want to hide code in a report?
    -   Why might someone want to show code in a report?

The only difference I saw was that the code chunk with the 2 + 2 did not pop-up when echo was set to equal FALSE. However, the calculation did still run. I feel like depending who the audience is you might want to hide or show the code.

# Part 3: A small R-in-markdown preview

-   Create a subsection within this section called About this document.
-   Write 2–3 sentences describing what this document is and what it produces.
-   Include one value generated by inline R code.

## About this Document

This document is an intro to using RMarkdown. I used headings, subheadings, among other functions to demonstrate my ability to use them. I demonstrated it by using one of my favorite quotes and directly linking it in the document. As well as showcasing some of Mac Miller's work by using lists. As well as using code chunks to be able to visualize what echo TRUE/FALSE can change when knitting a document.

`r Sys.Date()`


> To include inline code, use this weird little `r 2+2` pattern, putting the code where I have 2+2 (which is code!) You can use the function `Sys.Date()`, which would be added like this `r Sys.Date()` but you can do something else if you want. (Look at the knit html to see what this does.)

# Submitting Instructions

When you are finished:

-   Knit the document so that it produces an html file.
-   Stage, commit, and push:
    -   The updated `.rmd` file
    -   The generated `.html` file
-   Submit the GitHub link to the assignment on Canvas.
